---
title: "Lab 7 - Multiple Linear Regression"
author: "Samantha Kuglen"
date: "11/8/2021"
output: html_document
---

## Setup 
```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## Intro the ggpairs

Use GGgally::ggpairs() function to create a pairs plot
```{r}
ggpairs(penguins)
```

```{r}
# linear relationship appears to exist between body mass and other continuous variables
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>%  # use : to select across multiple columns
  ggpairs(aes(color = species))

```

## Omitted Variable Bias 
Important to look at data to know what data needs to be included. Include group as a variable to have correct models. 
```{r}
ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

## Multiple linear regression - penguins

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass).

```{r}
# Notation similar to simple linear regression
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# Return just the coefficients:
penguin_lm
```
Interpretting this coefficient for flipper length: on average, we would expect a 1 mm increase in flipper length to be associated with a 51.54 g increase in body mass if everything else about the penguins is constant.

Use summary() function to get more info
```{r}
# bill depth is the only one of not rejecting the null hypothesis, non-significant coefficient doesn't mean drop predictor variable from the model
summary(penguin_lm)
```
r-squared value of 0.7596 
We would expect that 75.96% of the variance in body weight in penguins can be explained by this model which consists of variables bill_depth_mm and flipper_length_mm. 

### Use `broom` functions tidy and glance

Use broom::tidy to get the coefficient summary in a data frame.
Use broom::glance to get the model summary in a data frame. 
```{r}
penguin_lm_tidy <- tidy(penguin_lm)
penguin_lm_tidy
```

Try using in-line code to refer to the bill-depth coefficient. Use command return to have value pop up.
`r penguin_lm_tidy$estimate[3]`

```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```

## Try another model

We have thought hard, done a literature review, consulted with experts, deeply explored our data and decided that the three most critical variables to include in this model (with body mass as the outcome variable) are:

- flipper length
- species
- sex

Task: create a multiple linear regression model using those 3 predictor variables 

Then take a look at the model outputs and interpret the coefficients

```{r}
body_mass_lm <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

body_mass_lm

# mass (g) = -365.82 + 20.02(flipp_mm) - 87.63(chinstrap) + 863.3(gentoo) + 530.38(male)
# For every 1 chinstrap penguin there is 
# Reference is female for sex and Adelie for species
# For every Gentoo penguin expect body mass to be 836.26g more than an Adelie penguin
# Chinstrap penguins are expected to be smaller than Adelie's by on average 87.63g for body mass
# Expect a male penguin to weigh on average 530.38 more than females

# Predic the mass of a penguin that has flipper length of 180 mm, chinstrap and is female.
# mass (g) = -365.82 + 20.02(180mm) - 87.63(1) + 863.3(0) + 530.38(0)
# set levels equal to 0 or 1

# Plug into equation to estimate male Adelie penguin 200m long flippers
# mass (g) = -365.82 + 20.02(200mm) - 87.63(0) + 863.3(0) + 530.38(1)
```

### Use broom:augment() to see predicted values
```{r}
# predicts values for existing observations
augment(body_mass_lm)
```

# Use plot to look at model diagnostics
```{r}
# Scale-Location: Relatively homogenous spread of variables?
# Independence of residuals: do errors of one variable impact errors of another observation
plot(body_mass_lm)
```

- Conceptual understanding and expertise allows me to responsibly determien that penguin species, sex and flipper length are reasonable predictor variables (thinking hard about variables and different variable combinations)

- Diagnostic plots all check out for normality of residuals, homoscedasticity, and now worrisome outliers (<< last one is not an assumption)


## Make output tables

Using model summary:
```{r}
modelsummary(body_mass_lm)
```

Using stargazer:
```{r, results = "asis"}
stargazer(body_mass_lm, type = "html")

```


